Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-09-29 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
fixed number of cores

```{r, scan1-{{hot_chr}}}
fn <- here::here("analysis", "data", "derived_data", "Chr{{hot_chr}}_scan1_out.rds")
if (file.exists(fn)) {
  s1out <- readRDS(fn)
} else {
  s1out <- qtl2::scan1(genoprobs = probs, 
                       pheno = cbind(hot_local, hot_nonlocal), 
                       kinship = K[["{{hot_chr}}"]], 
                       addcovar = covar, 
                       reml = TRUE, 
                       cores = 7
                       )
  saveRDS(s1out, fn)
}
```

```{r allele-effects-{{hot_chr}}}
fn <- here::here("analysis", "data", "derived_data", "Chr{{hot_chr}}_scan1coef_out.rds")
if (file.exists(fn)) {
  s1coef_out <- readRDS(fn)
} else {
s1coef_out <- purrr::map(.x = as_tibble(cbind(hot_local, hot_nonlocal)), 
           .f = function(pheno) {
             ph <- as.matrix(pheno)
             rownames(ph) <- rownames(expr)
             qtl2::scan1coef(genoprobs = list(probs[["{{hot_chr}}"]]), 
                             pheno = ph, 
                             kinship = K[["{{hot_chr}}"]], 
                             addcovar = covar, 
                             reml = TRUE, 
                             cores = 7
                             )
           }
                )
saveRDS(s1coef_out, fn)
}
```

>>>>

```{r, scan1-{{hot_chr}}}
fn <- here::here("analysis", "data", "derived_data", "Chr{{hot_chr}}_scan1_out.rds")
if (file.exists(fn)) {
  s1out <- readRDS(fn)
} else {
  s1out <- qtl2::scan1(genoprobs = probs, 
                       pheno = cbind(hot_local, hot_nonlocal), 
                       kinship = K[["{{hot_chr}}"]], 
                       addcovar = covar, 
                       reml = TRUE, 
                       cores = 1
                       )
  saveRDS(s1out, fn)
}
```

```{r allele-effects-{{hot_chr}}}
fn <- here::here("analysis", "data", "derived_data", "Chr{{hot_chr}}_scan1coef_out.rds")
if (file.exists(fn)) {
  s1coef_out <- readRDS(fn)
} else {
s1coef_out <- purrr::map(.x = as_tibble(cbind(hot_local, hot_nonlocal)), 
           .f = function(pheno) {
             ph <- as.matrix(pheno)
             rownames(ph) <- rownames(expr)
             qtl2::scan1coef(genoprobs = list(probs[["{{hot_chr}}"]]), 
                             pheno = ph, 
                             kinship = K[["{{hot_chr}}"]], 
                             addcovar = covar, 
                             reml = TRUE, 
                             cores = 1
                             )
           }
                )
saveRDS(s1coef_out, fn)
}
```
